Structural Divergence Analysis

### 2017-04-01 analysis-dynamical-nH.Rmd
dinamica

## profiles to compare
### square.dif.MSF
square.dif.MSF.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.square.dif.MSF.csv", sep = ""))
square.dif.MSF.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.square.dif.MSF.csv", sep = ""))
square.dif.MSF.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.square.dif.MSF.csv", sep = ""))

@@

```{r prepare_site_data}
# prepare the data
square.dif.MSF.exp = read.csv(square.dif.MSF.exp.fname, header = T)

square.dif.MSF.mut = read.csv(square.dif.MSF.mut.fname, header = T)

square.dif.MSF.medium = read.csv(square.dif.MSF.medium.fname, header = T)
```

### Dynamical divergence along sites

In this section we consider dynamical divergence using Cartessian coordinates. square.dif.MSF is the square diference between MSF of the proteins relative to the reference protein.

```{r comparisson-of-means}
# calculate means
mean.square.dif.MSF.exp = colMeans(square.dif.MSF.exp, na.rm = T)
mean.square.dif.MSF.mut = colMeans(square.dif.MSF.mut)
mean.square.dif.MSF.medium = colMeans(square.dif.MSF.medium)

# remove too divergent sites 
n.sites = length(mean.square.dif.MSF.exp)
mean.square.dif.MSF.exp = mean.square.dif.MSF.exp[-c(1,2,3,4,(n.sites-3), (n.sites-2), (n.sites-1), n.sites)]
mean.square.dif.MSF.mut = mean.square.dif.MSF.mut[-c(1,2,3,4,(n.sites-3), (n.sites-2), (n.sites-1), n.sites)]
mean.square.dif.MSF.medium = mean.square.dif.MSF.medium[-c(1,2,3,4,(n.sites-3), (n.sites-2), (n.sites-1), n.sites)]

# scale profiles
mean.square.dif.MSF.exp = rank(mean.square.dif.MSF.exp)
mean.square.dif.MSF.mut = rank(mean.square.dif.MSF.mut)
mean.square.dif.MSF.medium = rank(mean.square.dif.MSF.medium)

plot(mean.square.dif.MSF.exp, ylab = "Square dif MSF", xlab = "site", col = "blue")
points(mean.square.dif.MSF.mut, col = "green")
points(mean.square.dif.MSF.medium, col = "red")

r.exp.mut = cor(mean.square.dif.MSF.exp, mean.square.dif.MSF.mut)
r.exp.medium = cor(mean.square.dif.MSF.exp, mean.square.dif.MSF.medium)
r.mut.medium = cor(mean.square.dif.MSF.mut, mean.square.dif.MSF.medium)

@@

plot(x = mean.square.dif.MSF.exp, 
     y = mean.square.dif.MSF.mut, 
     xlab = "exp.mean.square.dif.MSF", 
     ylab = "mut.mean.square.dif.MSF")
abline(0, 1)

plot(x = mean.square.dif.MSF.exp, 
     y = mean.square.dif.MSF.medium, 
     xlab = "exp.mean.square.dif.MSF", 
     ylab = "medium.mean.square.dif.MSF")
abline(0, 1)

plot(x = mean.square.dif.MSF.mut, 
     y = mean.square.dif.MSF.medium, 
     xlab = "mut.mean.square.dif.MSF", 
     ylab = "medium.mean.square.dif.MSF")
abline(0, 1)
```

>>>>

## profiles to compare
### nH
nH.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.nH.csv", sep = ""))
nH.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.nH.csv", sep = ""))
nH.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.nH.csv", sep = ""))

@@

```{r prepare_site_data}
# prepare the data
nH.exp = read.csv(nH.exp.fname, header = T)

nH.mut = read.csv(nH.mut.fname, header = T)

nH.medium = read.csv(nH.medium.fname, header = T)
```

### Dynamical divergence along normal modes

In this section we consider dynamical divergence using normal modes coordinates.

```{r comparisson-of-means}
# calculate means
mean.nH.exp = colMeans(nH.exp, na.rm = T)
mean.nH.mut = colMeans(nH.mut)
mean.nH.medium = colMeans(nH.medium)

# scale profiles
mean.nH.exp = rank(mean.nH.exp)
mean.nH.mut = rank(mean.nH.mut)
mean.nH.medium = rank(mean.nH.medium)

plot(mean.nH.exp, ylab = "nH", xlab = "site", col = "blue")
points(mean.nH.mut, col = "green")
points(mean.nH.medium, col = "red")

r.exp.mut = cor(mean.nH.exp, mean.nH.mut)
r.exp.medium = cor(mean.nH.exp, mean.nH.medium)
r.mut.medium = cor(mean.nH.mut, mean.nH.medium)

@@

plot(x = mean.nH.exp, 
     y = mean.nH.mut, 
     xlab = "exp.mean.nH", 
     ylab = "mut.mean.nH")
abline(0, 1)

plot(x = mean.nH.exp, 
     y = mean.nH.medium, 
     xlab = "exp.mean.nH", 
     ylab = "medium.mean.nH")
abline(0, 1)

plot(x = mean.nH.mut, 
     y = mean.nH.medium, 
     xlab = "mut.mean.nH", 
     ylab = "medium.mean.nH")
abline(0, 1)
```

### 2017-04-01 analysis-dynamical-nR.Rmd
dinamica

## profiles to compare
### nH
nH.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.nH.csv", sep = ""))
nH.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.nH.csv", sep = ""))
nH.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.nH.csv", sep = ""))

@@

```{r prepare_site_data}
# prepare the data
nH.exp = read.csv(nH.exp.fname, header = T)

nH.mut = read.csv(nH.mut.fname, header = T)

nH.medium = read.csv(nH.medium.fname, header = T)
```

@@

```{r comparisson-of-means}
# calculate means
mean.nH.exp = colMeans(nH.exp, na.rm = T)
mean.nH.mut = colMeans(nH.mut)
mean.nH.medium = colMeans(nH.medium)

# scale profiles
mean.nH.exp = rank(mean.nH.exp)
mean.nH.mut = rank(mean.nH.mut)
mean.nH.medium = rank(mean.nH.medium)

plot(mean.nH.exp, ylab = "nH", xlab = "site", col = "blue")
points(mean.nH.mut, col = "green")
points(mean.nH.medium, col = "red")

r.exp.mut = cor(mean.nH.exp, mean.nH.mut)
r.exp.medium = cor(mean.nH.exp, mean.nH.medium)
r.mut.medium = cor(mean.nH.mut, mean.nH.medium)

@@

plot(x = mean.nH.exp, 
     y = mean.nH.mut, 
     xlab = "exp.mean.nH", 
     ylab = "mut.mean.nH")
abline(0, 1)

plot(x = mean.nH.exp, 
     y = mean.nH.medium, 
     xlab = "exp.mean.nH", 
     ylab = "medium.mean.nH")
abline(0, 1)

plot(x = mean.nH.mut, 
     y = mean.nH.medium, 
     xlab = "mut.mean.nH", 
     ylab = "medium.mean.nH")
abline(0, 1)
```

>>>>

## profiles to compare
### nR
nR.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.nR.csv", sep = ""))
nR.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.nR.csv", sep = ""))
nR.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.nR.csv", sep = ""))

@@

```{r prepare_site_data}
# prepare the data
nR.exp = read.csv(nR.exp.fname, header = T)

nR.mut = read.csv(nR.mut.fname, header = T)

nR.medium = read.csv(nR.medium.fname, header = T)
```

@@

```{r comparisson-of-means}
# calculate means
mean.nR.exp = colMeans(nR.exp, na.rm = T)
mean.nR.mut = colMeans(nR.mut)
mean.nR.medium = colMeans(nR.medium)

# scale profiles
mean.nR.exp = rank(mean.nR.exp)
mean.nR.mut = rank(mean.nR.mut)
mean.nR.medium = rank(mean.nR.medium)

plot(mean.nR.exp, ylab = "nR", xlab = "site", col = "blue")
points(mean.nR.mut, col = "green")
points(mean.nR.medium, col = "red")

r.exp.mut = cor(mean.nR.exp, mean.nR.mut)
r.exp.medium = cor(mean.nR.exp, mean.nR.medium)
r.mut.medium = cor(mean.nR.mut, mean.nR.medium)

@@

plot(x = mean.nR.exp, 
     y = mean.nR.mut, 
     xlab = "exp.mean.nR", 
     ylab = "mut.mean.nR")
abline(0, 1)

plot(x = mean.nR.exp, 
     y = mean.nR.medium, 
     xlab = "exp.mean.nR", 
     ylab = "medium.mean.nR")
abline(0, 1)

plot(x = mean.nR.mut, 
     y = mean.nR.medium, 
     xlab = "mut.mean.nR", 
     ylab = "medium.mean.nR")
abline(0, 1)
```
